Some Graphical Realizations of Two-Row Specht Modules of Iwahori--Hecke Algebras of the Symmetric Group

### 2019-07-31 tex/Drafts/Draft-3-addressingKernelComments.tex
addressed section 3.1 comments

{\color{magenta} \Huge PLEASE ADDRESS: $W$ needs to be replaced with $M$.} 
{\color{magenta} Also, titles should be lower case (I fixed in this document), and can be more descriptive\ldots e.g. ``Sign subrepresentations of the crossingless matching; characterizing the sign subrepresentation; Sign subrepresentations when e = n+r+1.}

@@

For compactness, in this section we use $\sim $ to denote ``proportional to." For convenience, define $M_0^0$ and $M_1^1$ to be the zero representation. Note that in this section, as well as later sections characterizing the sign subrepresentation, we do not assume $n>0$.

@@

		\item Define the \emph{rainbow element} $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left followed by a ``rainbow" to the right.
	\end{itemize}

@@

\begin{figure} 
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\GeneralizedMatching{8}{3/8, 4/7, 5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
		\Matching{4}{1/4, 2/3}
		\end{gathered}}$
	\caption{The rainbow element $R\in M_8^2$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. The nodes $R(4)=7$, $R(5)=6$, so $R(4,7)$ defines a sub-matching. Specifically, $R(4,7)=\sigma$. Alternatively, $R(3)=8$, so, for instance $R(2,7)$ is not a sub-matching, and refers to the ordered set $(2,8,7,6,5,4)$. $R(2,1)$ is an element of the zero representation since $2>1$.}
	\label{sub-matching example}
\end{figure}

@@

\begin{proof}
	Let $W$ be the set of basis elements with nonzero coordinate in $w$. Let $z$ be the maximal number of anchors to the far left in any element $\psi\in W$. Formally, $z$ is the greatest positive integer such that there exists some element $\psi\in W$ satisfying $\psi(1)-1=...=\psi(z)-z=0$. For some positive integer $j$ define $W^j\subset W$ to be the set of all basis elements in $W$ with $j$ anchors to the far left.

	Suppose $z<r$. Then for each $\psi\in W^z$, exactly $z$ anchors are positioned to the far left, so we may define $i_\psi$ to be the position of the next leftmost anchor in $\psi$. Fix some $\widehat{\psi}\in W^z$ such that $i_{\widehat{\psi}}\leq i_\psi$ for all $\psi$.

@@

	Immediately, we may intuit a few properties of $\psi'$:
	\begin{enumerate}[label={(\roman*)}]
		\item $\psi'$ still has $z$ anchors on the left.
		\item Defining $i_{\psi'}$ to be the next leftmost anchor, $i_{\psi'}<i_{\widehat{\psi}}$
	\end{enumerate}

@@

	Define $\sigma':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma$.If $\sigma\not\in W^z$, $\sigma'$ will have $z$ anchors at the far left only if $\sigma'\in W^{z-1}$ and the $z$th leftmost anchor is at position $i_{\widehat{\psi}}$. But then the position of the $z+1$st anchor is unchanged by the action, and must be at position greater than $i_{\widehat{\psi}}$, so from (ii) $\sigma'\not=\psi'$. If $\sigma\in W^z$, $\sigma'$ will have anchor at $i_{\psi'}$ if and only if $i_\sigma=i_{\widehat{\psi}}$ and $\sigma(i_{\widehat{\psi}}-1)=\widehat{\psi}(i_{\widehat{\psi}}-1)$. Since these are the only three indices altered by action of $(1+T_{i_{\widehat{\psi}}-1})$ on $\sigma$, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$ this implies $\sigma=\widehat{\psi}$ as desired. So if $z<r$ $w$ is not in the desired kernel.

	\vspace{1mm}
	We have proven that there exists an element in $W$ with all anchors to the far left, or equivalently that $W^r$ is nonempty. Now we must prove that $R\in W^r$. The proof is analogous to the previous case. First we define subsets $W^r_j\subset W^r$ that have the top $j$ arcs of the rainbow, and define $y$ to be the most arcs any element has. In the previous proof, we showed that if we move the next left-most anchor further left, the image of $w$ under that transposition will be nonzero. In this proof, we will show that if we expand the next-largest arc, the image of $w$ under that transposition will be nonzero.

	\vspace{1mm}
	Suppose $z=r$ but $R\not\in W^r$ (so $R\not\in W$). Let us define a sequence of subsets $W^r_i\subset W^r$ to be the set of elements in $W^r$ with the top $i$ humps of the rainbow. Formally, $W^r_0:=W^r$, $W^r_{i+1}:=\{\upsilon\in W^r_i| \upsilon(r+i+1)=2n+r-i \}$. Since $R\not\in W^r$,  there exists some positive integer $y$ less than $n-1$ such that $W^r_{y+1}=\emptyset$; $y$ is the largest number of contiguous top level rainbow humps that any element in $W^r$ has.

@@

Given a rainbow element $R$, define the basis elements $R_{R,i},R_{L,i}$ to be those where you move the middle hump across $i$ lines to the right or left, respectively. Examples are pictured in \ref{shifted rainbow}. Formally, $R_{R,i}:=q^{-i/2}(1+T_{r+n+i})...(1+T_{r+n+1})R$, $R_{L,i}:=q^{-i/2}(1+T_{r+n-i})...(1+T_{r+n-1})R$.

\begin{figure}
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\Matching{8}{1/8, 2/7, 3/6, 4/5}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/7, 3/4, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/8, 2/3, 4/7, 5/6}, \hspace{\cbasisspacing}
		\Matching{8}{1/2,3/8,4/7,5/6}
		\end{gathered}}$
	\caption{$R_{L,0},...,R_{L,3}$ pictured from left to right}
	\label{shifted rainbow}
\end{figure}

Define $Q_n:=(q^n+...+1)/q^{n/2}(-1)^n$ for $n\in \{0,1,...\}$. The following proposition says that, for any element in the kernel, if some basis element $y$ has coordinate $c$ in that element, and if $y$ has a rainbow sub-matching, the basis elements where you replace that sub-matching by the shifted rainbow matchings $R_{L,i}$ or $R_{R,i}$ both have coordinate $Q_ic$ in the kernel element.

\begin{proposition}
	Let $w$ be an element in the kernel intersection $\cap (1+T_z)$ in some generalized crossingless matchings representation. Let $y$ be a basis element with coordinate $c$ in $w$. Suppose $\exists a,b$ such that $y(a,b)=R$, the rainbow element. Define the basis elements $\theta_i,\phi_i$ by $\theta_i(1,a-1)=\phi(1,a-1)=y(1,a-1)$, $\theta_i(b+1,2n)=\phi(b+1,2n)=y(b+1,2n)$, $\theta_i(a,b)=R_{R,i}$, $\phi_i(a,b)=R_{L,i}$ (leave $\theta_i$ or $\phi_i$ undefined for any $i$ where $R_{R,i},R_{L,i}$ are undefined, respectively). The coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.

@@

Proof of this proposition requires a simple algebraic fact that will be used throughout this document, so I state it as a lemma.

\begin{lemma}
	$Q_1Q_n-Q_{n-1}=Q_{n+1}$

@@

\textit{Proof of lemma.}

\begin{align*}
Q_1Q_n-Q_{n-1}=&\frac{-(q+1)}{q^{1/2}}\frac{(-1)^n(q^n+...+1)}{q^{n/2}}-\frac{(-1)^{n-1}(q^{n-1}+...+1)}{q^{(n-1)/2}}\\
=&\frac{(-1)^{n+1}(q^{n+1}+2q^n+...+2q+1)}{q^{(n+1)/2}}-\frac{(-1)^{n+1}(q^n+...+q)}{q^{(n+1)/2}}\\
=&\frac{(-1)^{n+1}(q^{n+1}+...+1)}{q^{(n+1)/2}}=Q_{n+1}
\end{align*}

Now let us prove the proposition.

\begin{proof}
	Consider acting on $w$ by an element $(1+T_z)$. The coordinate of $\phi_i$ in $(1+T_z)w$ will be a linear combination of the coordinates of basis elements sent to $\phi_i$ by the element $(1+T_z)$. Specifically, it will be $(1+q)c\iota+(q^1/2)\sum c_\psi$ where $\iota=1$ if $y(z)=z+1$, $\iota=0$ otherwise, and $c_\psi$ are the coordinates of all basis elements $\psi$ where $(1+T_z)\psi\sim y$.

	Let $n:=a+b-1$ and $r$ be the number of anchors in $y(a,b)$. Consider the coordinate of $\phi_i$ in $(1+T_{a-1+r+n/2-i})w$. This is the transposition that acts on the "moved middle hump" in $\phi_i(a,b)=R_{L,i}$, as shown in \ref{shifted relations}. I claim the following:

	\begin{center}
		\textit{claim}:
		The only basis elements $\psi$ where $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$ are $\phi_i$ and $\phi_{i-1},\phi_{i+1}$ when they exist\footnote{we defined $R_{L,i}$ as far out as we can move the hump, so for $0\leq i<n+r$, and take the analogous domain for $\phi_i$}.

	\end{center}

	Note that the action of any $(1+T_z)$ on a basis element $\psi$ creates exactly two lines: an arc of length two connecting $z$ and $z+1$, and either an anchor or an arc of length $\geq 2$ connecting $\psi(z)$ and $\psi(z+1)$.\footnote{Although this fact follows directly from our definition of the representation, it will be used throughout the document, so it is important that the reader understands it.\label{two humps created}} The easiest way to see the claim is to see that the given transposition is surrounded by arcs on both sides, so any basis element sent to the same element can vary from $\phi_i$ by at most one of those arcs and nothing else.

	Let us prove the claim formally: It is easy to see that the action of $(1+T_{a-1+r+n/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\sim \phi$, as shown in \ref{shifted relations}. Suppose there was another basis element $\psi$ sent to $\phi_i$ by the given transposition. Me note that if $\psi$ contains the arcs or anchors directly to the right and left of the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ in $\phi_i$ (formally, it contains the arc $(a-1+r+n/2-i-1,a-1+r+n/2+i+2)$ or an anchor at $a-1+r+n/2-i-1$ and the arc $(a-1+r+n/2-i+2,a-1+r+n/2+i+1)$ or an anchor at $a-1+r+n/2-i+2$), it must contain the arc $(a-1+r+n/2-i,a-1+r+n/2-i+1)$ to be a crossingless matching. Thus, if $\psi$ contains both of these arcs/anchors, $(1+T_{a-1+r+n/2-i})$ acts as the constant $(1+q)$, so $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i=>\psi\sim \phi$. If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r+n/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r+n/2-i})$ must create that arc/anchor, so $\psi(a-1+r+n/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r+n/2-i+1)=a-1+r+n/2+i+2$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor. All other matchings remain unchanged, so this implies $\psi=\phi_{i+1}$. Likewise, if the right arc $((a+b-1)/2-i+2,(a+b-1)/2+i+1)$ does not exist, $\psi=\phi_{i-1}$. For boundary cases, note that for $\phi_0=\theta_0$, the only other basis element sent to this by the middle transposition is $\phi_1=\theta_1$. Also note that at the edge case $\phi_{n+r-1}$ there is not necessarily a left arc, so other elements may be sent to $\phi_{n+r-1}$ by the given transposition, and this case gives no new information. Lastly, note that our argument was completely symmetric and thus applies to the $\theta_i$ case, except that for $\theta_i$ we do not have to deal with anchors. Thus the claim is proved.

	Given this claim and lemma \ref{Q alg}, the proposition follows quickly through induction:

	Acting by $(1+T_{a-1+r+n/2})$ on $w$, the new coordinate of $\phi_0=y$ is $(q+1)c+q^{1/2}c_{\phi_1}$ where $c_{\phi_1}$ is the coordinate of $\phi_1$ in $w$. Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$. $\phi_1=\theta_1$ so this gives us all our base cases.

	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$. By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_i=0$ so $c_{\phi_{i+1}}=Q_1Q_i-Q_{i-1}=Q_{i+1}$ by lemma \ref{Q alg}. $\theta_i$ is an identical proof, so the proposition follows.

	\begin{figure}
		\[
		\GeneralizedAction{8}{3/4,5/8,6/7}{2}{1/1,2/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{(1+q)}
		\]
		\[
		\GeneralizedAction{8}{2/3,5/8,6/7}{2}{1/1,4/2}{1}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
		\]
		\[
		\GeneralizedAction{8}{3/8,4/5,6/7}{2}{1/1,2/2}{1.25}{3}{3/4,5/8,6/7}{1/1,2/2}{q^{1/2}}
		\]
		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i=1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y$ is the rainbow vector in $M_{8}^2$ and $i=2$.}
		\label{shifted relations}
	\end{figure}
\end{proof}

@@

	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$. Using the same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that if a basis element $\psi$ has no anchor at position $3$ and is not equal to $R_{L,n+r-2}$, $(1+T_1)\psi\not\sim R_{L,n+r-1}$. Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}. Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$. Me have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$. Thus we have arrived at contradiction, and $K=0$.
\end{proof}

@@

 \begin{proof}
 	Suppose $\psi(1)=a$. The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ humps then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.

@@

 		$\cbr{
 			\begin{gathered}
 			\GeneralizedMatching{8}{3/8, 4/7,5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 5/8,6/7}{2}{3/1,4/2}{5/4}, 
 			\hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 3/4,7/8}{2}{5/1,6/2}{5/4}, \hspace{\cbasisspacing}
 			\end{gathered}}$ 
 		\caption{In order, the rainbow element, $R_1$, and $R_2$. The coordinate of the rainbow element is 1. The coordinate of $R_1$ is $Q_{4}$. The coordinate of $R_2$ is $Q_4Q_3$. Generally, $R_i$ is the element with $i$ humps then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
 	\end{figure}

@@

 		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level humps, including the leftmost anchor.

>>>>

@@

For compactness, in this section we use $\sim $ to denote ``proportional to." For convenience, define $M_0^0$ and $M_1^1$ to be the zero representation. Note that in this subsection, as well as section \ref{Sign section}, we do not assume $n>0$.

@@

		\item Define the \emph{rainbow element} $R\in M_{2n+r}^r$ to be the basis element specified by $R(i)=2n+2r-i+1$ for $i>r$, $R(i)=i$ for $i\leq r$. In other words, the basis element with all anchors to the left followed by a ``rainbow" to the right.

		\item Define a \emph{rainbow sub-matching} to be a sub-matching $\psi(a,b)$ corresponding to some rainbow element and satisfying the following property: if $a$ is an anchor then $b=2n+r$. This definition is motivated by the isotopy mentioned illustrated in diagram \ref{Branching commutative diagram}.
	\end{itemize}

@@

\begin{figure} 
	\def\cbasisspacing{5mm}
	$\cbr{
		\begin{gathered}
		\GeneralizedMatching{8}{3/8, 4/7, 5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
		\Matching{4}{1/4, 2/3}
		\end{gathered}}$
	\caption{The rainbow element $R\in M_8^2$ is pictured on the left, $\sigma\in M_4^0$ is pictured on the right. The nodes $R(4)=7$, $R(5)=6$, so $R(4,7)$ defines a sub-matching. Specifically, $R(4,7)$ is a rainbow sub-matching, and $R(4,7)=\sigma$. Alternatively, $R(3)=8$, so, for instance $R(2,7)$ is not a sub-matching, and refers to the ordered set $(2,8,7,6,5,4)$. $R(2,1)$ is an element of the zero representation since $2>1$.}
	\label{sub-matching example}
\end{figure}

@@

\begin{proof}
	Let $W$ be the set of basis elements with nonzero coordinate in $w$. First, we will prove that $W$ contains an element with all anchors to the far left. Then we will apply the same argument to prove $W$ contains the rainbow element.

	Let $z$ be the maximal number of anchors to the far left in any element $\sigma\in W$. Formally, $z$ is the greatest positive integer such that there exists some element $\sigma\in W$ satisfying $\sigma(1)-1=...=\sigma(z)-z=0$. For any positive integer $j$ define $W^j\subset W$ to be the set of all basis elements in $W$ with $j$ anchors to the far left.

	Suppose $z<r$. Then for each $\psi\in W^z$, exactly $z$ anchors are positioned to the far left, so we may define $i_\psi$ to be the position of the next leftmost anchor in $\psi$. In other words, $i_y$ is the position of the $z+1$st anchor from the left in $\psi$. Fix some $\widehat{\psi}\in W^z$ such that $i_{\widehat{\psi}}\leq i_\psi$ for all $\psi$.

@@

	Immediately, we may intuit a few properties of $\psi'$:
	\begin{enumerate}[label={(\roman*)}]
		\item $\psi'$ still has $z$ anchors on the left.
		\item Defining $i_{\psi'}$ to be the position of the next leftmost anchor, $i_{\psi'}<i_{\widehat{\psi}}$
	\end{enumerate}

@@

	Define $\sigma':=q^{-1/2}(1+T_{i_{\widehat{\psi}}-1})\sigma$. Note that the action of $(1+T_{i_{\widehat{\psi}}-1})$ changes exactly two matches in $\sigma$, and these matches must involve the nodes $i_{\widehat{\psi}}-1,i_{\widehat{\psi}}$. It follows that if $\sigma\not\in W^z$, $\sigma'$ will have $z$ anchors at the far left only if $\sigma'\in W^{z-1}$ and the $z$th leftmost anchor is at position $i_{\widehat{\psi}}$. But then the position of the $z+1$st anchor is unchanged by the action, and must be at position greater than $i_{\widehat{\psi}}$, so from (ii) $\sigma'\not=\psi'$. If $\sigma\in W^z$, $\sigma'$ will have anchor at $i_{\psi'}$ if and only if $i_\sigma=i_{\widehat{\psi}}$ and $\sigma(i_{\widehat{\psi}}-1)=\widehat{\psi}(i_{\widehat{\psi}}-1)$. Since these are the only three indices altered by action of $(1+T_{i_{\widehat{\psi}}-1})$ on $\sigma$, if $(1+T_{i_{\widehat{\psi}}-1})\sigma\sim \psi'$ this implies $\sigma=\widehat{\psi}$ as desired. So, if $z<r$, $w$ is not in the desired kernel.

	\vspace{2mm}
	We have proven that there exists an element in $W$ with all anchors to the far left, or equivalently that $W^r$ is nonempty. Now we must prove that $R\in W^r$. The proof is analogous to the previous case. First we define subsets $W^r_j\subset W^r$ that have the top $j$ arcs of the rainbow, and define $t$ to be the most arcs any element has. Previously, we showed that if we move the next left-most anchor further left, the image of $w$ under that transposition will be nonzero. Now, we will show that if we expand the next-largest arc, the image of $w$ under that transposition will be nonzero.

	\vspace{2mm}
	Suppose $z=r$ but $R\not\in W^r$ (so $R\not\in W$). Let us define a sequence of subsets $W^r_j\subset W^r$ to be the set of elements in $W^r$ with the top $j$ arcs of the rainbow. Formally, $W^r_0:=W^r$, $W^r_{j+1}:=\{\upsilon\in W^r_j| \upsilon(r+j+1)=2n+r-j \}$. Since $R\not\in W^r$,  there exists some positive integer $t$ less than $n-1$ such that $W^r_{t+1}=\emptyset$; $t$ is the largest number of contiguous top level rainbow arcs that any element in $W^r$ has.

@@

\vspace{3mm}
\begin{definition}
	Given a rainbow element $R$, define the \emph{shifted rainbow elements} $R_{R,i},R_{L,i}$ to be those where you ``move the 'length two middle arc' across $i$ lines to the right or left, respectively." This is made clear in figure \ref{shifted rainbow}. Formally: $$R_{R,i}:=q^{-i/2}(1+T_{r+n+i})\cdots(1+T_{r+n+1})R$$, $$R_{L,i}:=q^{-i/2}(1+T_{r+n-i})\cdots(1+T_{r+n-1})R$$.
\end{definition}

\begin{figure}
	\def\cbasisspacing{2mm}
		\begin{adjustbox}{width=\textwidth}
		\GeneralizedMatching{9}{2/9, 3/8, 4/7, 5/6}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
		\GeneralizedMatching{9}{2/9, 3/8, 4/5, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
		\GeneralizedMatching{9}{2/9, 3/4, 5/8, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
		\GeneralizedMatching{9}{2/3,4/9,5/8, 6/7}{1}{1/1}{7/4}, \hspace{\cbasisspacing}
		\GeneralizedMatching{9}{1/2, 4/9,5/8, 6/7}{1}{3/1}{7/4}
		\end{adjustbox}
	\caption{$R_{L,0},...,R_{L,4}$ pictured from left to right. If $w\in K_{9}^1$ and $R=R_{L,0}$ has coordinate $c$ in $w$, then proposition \ref{shifted rainbow coeffs} claims $R_{L,1}$ has coordinate $Q_1$, $R_{L,2}$ has coordinate $Q_2$, etc.}
	\label{shifted rainbow}
\end{figure}

\begin{definition}
	The following $q$-number deformation will be integral to this subsection and section \ref{Sign section}:

		 $$Q_n:=(-1)^n\frac{q^n+\ldots+1}{q^{n/2}} \text{ for }n \text{ a nonnegative integer}$$. 
\end{definition}

The following proposition applies to any basis element $y$ with a rainbow sub-matching. It says that if $y$ has coordinate $c$ in $w\in K$, then those elements $\theta_i,\phi_i$, where you replace the rainbow sub-matching with a ``shifted rainbow sub-matching" $R_{R,i}$ or $R_{L,i}$, have coordinate $Q_ic$ in $w$. An example is given in figure \ref{shifted rainbow}.

\begin{proposition}
	Let $w\in K^r_{2n+r}$. Let $y$ be a basis element with coordinate $c$ in $w$. Suppose that there exist $a,b$ such that $y(a,b)$ is a rainbow sub-matching. Define the basis elements $\theta_i,\phi_i$ to be those elements where we replace the rainbow sub-matching with a shifted rainbow sub-matching. Formally: $$\theta_i(1,a-1):=\phi(1,a-1):=y(1,a-1)\text{ ,}$$
	$$\theta_i(b+1,2n):=\phi(b+1,2n):=y(b+1,2n)\text{ ,}$$ 
	$$\theta_i(a,b)=R_{R,i}\text{ ,}$$ $$\phi_i(a,b)=R_{L,i}\text{.}$$

	We restrict $i$ in $\theta_i,\phi_i$ to be such that $R_{R,i},R_{L,i}$ are defined, respectively.

	Then the coordinates of $\phi_i$ and $\theta_i$ in $w$ are both $Q_ic$.

@@

We will use the following algebraic lemma to prove this proposition. The lemma will also be useful in section \ref{Sign section}.

\begin{lemma}
	$Q_1Q_n-Q_{n-1}=Q_{n+1}$ for $n>0$.

@@

\begin{proof}[Proof of lemma]
	We compute:
\begin{align*}
Q_1Q_n-Q_{n-1}=&\prn{-\frac{(q+1)}{q^{1/2}}}\prn{(-1)^n\frac{(q^n+\cdots+1)}{q^{n/2}}}-(-1)^{n-1}\frac{(q^{n-1}+\cdots+1)}{q^{(n-1)/2}}\\
=&(-1)^{n+1}\frac{(q^{n+1}+2q^n+\cdots+2q+1)}{q^{(n+1)/2}}-(-1)^{n+1}\frac{(q^n+\cdots+q)}{q^{(n+1)/2}}\\
=&(-1)^{n+1}\frac{(q^{n+1}+\cdots+1)}{q^{(n+1)/2}}\\
=&Q_{n+1}
\end{align*}
\end{proof}
Now let us prove the proposition.

\vspace{1.5mm}
\textit{\label{two humps created}Note: This proof relies on the simple fact that the action of a transposition $(1+T_i)$, assuming it does not send an element to zero, will update exactly two matches if it is changes the element. This follows directly from our definition of the representation, and will be integral to many proofs in this document.}

\vspace{1.5mm}
\begin{proof}

	First, we will show that if we act by the transposition corresponding to the moved arc in $\phi_i$, the only basis elements sent to $\phi_i$ are $\phi_{i-1}$, $\phi_{i}$, and $\phi_{i+1}$. We will show that the analogous statement is true for $\theta_i$, and use this to finish the proof by induction. Formally:

	\begin{claim*}
		Suppose $\psi\in M_{2n+r}^r$ is a basis element. Take $i$ such that $\phi_i$, $\phi_{i-1}$, and $\phi_{i+1}$ are all defined. Let $2n'+r'$, $r'$ be the number of nodes and anchors in $y(a,b)$, respectively. Then $(1+T_{a-1+r'+n'/2-i})\psi\sim \phi_i$ implies $\psi=\phi_i$, $\phi_{i-1}$, or $\phi_{i+1}$.

		Similarly, taking $i$ such that $\theta_i$, $\theta_{i-1}$, and $\theta_{i+1}$ are all defined, $(1+T_{a-1+r'+n'/2+i})\psi\sim \phi_i$ implies $\psi=\phi_i$, $\phi_{i-1}$, or $\phi_{i+1}$.
	\end{claim*}

	Note that $a-1+r'+n'/2-i$ is simply the starting node of the moved arc in $\phi_i$.

	For the entirety of the proof of this claim, it will be instructive to reference Figure \ref{shifted relations} as an example.

	It is easy to see that the action of $(1+T_{a-1+r'+n'/2-i})$ will bring $\phi_{i-1},\phi_i,\phi_{i+1}$ to $\phi$. Suppose there exists another basis element $\psi$ sent to $\phi_i$ by the given transposition. Consider the arcs (or anchors) starting just inside and just outside of the moved arc in $\phi_i$: these are the arcs $(a-1+r'+n'/2-i-1,\phi_i(a-1+r'+n'/2-i-1))$ and $(a-1+r'+n'/2-i+2,\phi_i(a-1+r'+n'/2-i+2))$.

	If $\psi$ contains both of these arcs, it must contain the arc $(a-1+r'+n'/2-i,a-1+r'+n'/2-i+1)$ to be a crossingless matching. This follows from our definition of rainbow sub-matching in definition \ref{sub-matchings}. Thus $\psi$ is fixed by the action of $(1+T_{a-1+r'+n'/2-i})$, so $\psi=\phi_i$.

	If $\psi$ does not contain the left arc/anchor and $(1+T_{a-1+r'+n'/2-i})\psi\sim \phi_i$, the action of $(1+T_{a-1+r'+n'/2-i})$ must create that arc/anchor. Thus $\psi(a-1+r'+n'/2-i-1)=a-1+r+n/2-i$ and $\psi(a-1+r'+n'/2-i+1)=\phi_i(a-1+r'+n'/2-i-1)$ in the case of an arc or $a-1+r+n/2-i+1$ is an anchor. These matchings are identical to those of $\phi_{i+1}$, and no other matchings are changed by the action, so $\psi=\phi_{i+1}$. Likewise, if $\psi$ does not contain the right arc/anchor, that arc/anchor must be created by the action of $(1+T_{a-1+r'+n'/2-i})$, so $\psi=\phi_{i-1}$.

	Lastly, note that the above argument was completely symmetric with respect to the parity of $i$, and hence an analogous argument without anchors handles the $\theta_i$ case. Thus the claim is proved.

	\vspace{2mm}
	As an edge case related to the claim, note that the only basis element sent to $y=\phi_0=\theta_0$ other than itself by the transposition acting on the middle of the rainbow is $\theta_1=\phi_1$ if they both exist. Otherwise, just $\phi_1$ exists and is sent to $y$, or the rainbow element has two nodes and neither exist.

	We finish the proof of the proposition through induction:

	Acting by $(1+T_{a-1+r+n/2})$ on $w$, the new coordinate of $\phi_0=y$ is $(q+1)c+q^{1/2}c_{\phi_1}$ where $c_{\phi_1}$ is the coordinate of $\phi_1$ in $w$. Since $w$ is in the kernel, we have $(q+1)c+q^{1/2}c_{\phi_1}=0=>c_{\phi_1}=Q_1c$. Since $\phi_1=\theta_1$, this gives us all our base cases.

	Acting by $(1+T_{a-1+r+n/2-i})$ on $w$, the new coordinate of $\phi_i$ is $q^{1/2}c_{\phi_{i+1}}+q^{1/2}c_{\phi_{i-1}}+(q+1)c_{\phi_{i}}=0$. By the inductive hypothesis, $q^{1/2}c_{\phi_{i+1}}+q^{1/2}Q_{i-1}c+(q+1)Q_ic=0$ so $c_{\phi_{i+1}}=Q_1Q_ic-Q_{i-1}c=Q_{i+1}c$ by lemma \ref{Q alg}. The case of $\theta_i$ is an identical proof, so the proposition follows.

	\begin{figure}
		\[
		\GeneralizedAction{10}{1/2,5/6,7/10,8/9}{2}{3/1,4/2}{1}{5}{1/2,5/6,7/10,8/9}{3/1,4/2}{(1+q)}
		\]
		\[
		\GeneralizedAction{10}{1/2,5/10,6/7,8/9}{2}{3/1,4/2}{1}{5}{1/2,5/6,7/10,8/9}{3/1,4/2}{q^{1/2}}
		\]
		\[
		\GeneralizedAction{10}{1/2,4/5,7/10,8/9}{2}{3/1,6/2}{1}{5}{1/2,5/6,7/10,8/9}{3/1,4/2}{q^{1/2}}
		\]
		\caption{The action of $(1+T_{a-1+r+n/2-i})$ on $\phi_i,\phi_{i-1},\phi_{i+1}$ (ordered from top to bottom), shown as the case where $y(3,10)$ is the rainbow vector in $M_{8}^2$ and $i=2$. When both the first anchor and top level rainbow arc are intact, the arc of the transposition must also exist. When one of these is broken, there is only one way to fix it.}
		\label{shifted relations}
	\end{figure}
\end{proof}

@@

	Consider the coordinate of $R_{L,n+r-1}$ in $(1+T_1)w$. By the exact same logic as in the proof of proposition \ref{shifted rainbow coeffs}, we note that the only basis elements sent to $R_{L,n+r-1}$ by action of $(1+T_1)$ are itself and $R_{L,n+r-2}$. Thus the desired coordinate is equal to $(1+q)Q_{n+r-1}c+q^{1/2}Q_{n+r-2}c=-q^{1/2}Q_{n+r}c$ by lemma \ref{Q alg}.

	Since $w\in K$, we must have $-q^{1/2}Q_{n+r}c=0$. We have that $c$ is nonzero, and we assume $q$ nonzero, and $Q_{n+r}$ is zero iff $q$ is a root of $q^{n+r}+...+1$, implying $e|n+r+1$. Thus we have arrived at contradiction, and $K=0$.
\end{proof}

@@

 \begin{proof}
 	Suppose $\psi(1)=a$. The proof is structured as follows: use proposition \ref{shifted rainbow coeffs} to find the coefficient of the basis element with $\lfloor a/2\rfloor$ length two arcs then a rainbow element; use the same proposition in a reversed manner to find the coefficient of the basis element consisting of the rainbow for the first $a$ nodes, then the rainbow for the final $2n+r-a$ nodes; finally, we finish the proof through induction using lemma \ref{sub-matching isomorphism}.

@@

 		$\cbr{
 			\begin{gathered}
 			\GeneralizedMatching{8}{3/8, 4/7,5/6}{2}{1/1,2/2}{5/4}, \hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 5/8,6/7}{2}{3/1,4/2}{5/4}, 
 			\hspace{\cbasisspacing}
 			\GeneralizedMatching{8}{1/2, 3/4,7/8}{2}{5/1,6/2}{5/4}, \hspace{\cbasisspacing}
 			\end{gathered}}$ 
 		\caption{In order, the rainbow element, $R_1$, and $R_2$. The coordinate of the rainbow element is 1. The coordinate of $R_1$ is $Q_{4}$. The coordinate of $R_2$ is $Q_4Q_3$. Generally, $R_i$ is the element with $i$ length two arcs then a rainbow element, and has coordinate $Q_{n+r-1}...Q_{n+r-i}$.}
 	\end{figure}

@@

 		Me will prove this equality through yet another inductive proof, this time inducting on the number of top level arcs, including the leftmost anchor.
